Bioverse: Origins of Life

### 2024-06-11 src/tex/ms.tex
fix units

\subsubsection{expected biosignature pattern in a transit survey}
A representative recovery of the injected biosignature pattern is shown in Figure~\ref{fig:detections_uv}.
There, we assumed an abiogenesis rate of $f_\mathrm{life} = \var{f_life}$ and a minimum \gls{NUV} flux of $F_\mathrm{NUV, min} = \var{NUV_thresh}\,\SI{}{\photons\per\centi\meter\squared\per\second\per\nano\meter}$.
This leads to a distribution of biosignature detections with detections increasingly occurring above a threshold inferred NUV flux.
\begin{figure}
    \script{detections_uv.py}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/detections_uv}
        \caption{Recovered biosignature detections in the \gls{NUV} flux -- biosignature occurrence space. The dashed line denotes the threshold \gls{NUV} flux $F_\mathrm{NUV, min}$.}
        \label{fig:detections_uv}
    \end{centering}
\end{figure}

>>>>

\subsubsection{expected biosignature pattern in a transit survey}
A representative recovery of the injected biosignature pattern is shown in Figure~\ref{fig:detections_uv}.
There, we assumed an abiogenesis rate of $f_\mathrm{life} = \var{f_life}$ and a minimum \gls{NUV} flux of $F_\mathrm{NUV, min} = \var{NUV_thresh}\,\SI{}{\erg\per\second\per\centi\meter\squared}$.
This leads to a distribution of biosignature detections with detections increasingly occurring above a threshold inferred NUV flux.
\begin{figure}
    \script{detections_uv.py}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/detections_uv}
        \caption{Recovered biosignature detections in the \gls{NUV} flux -- biosignature occurrence space. The dashed line denotes the threshold \gls{NUV} flux $F_\mathrm{NUV, min}$.}
        \label{fig:detections_uv}
    \end{centering}
\end{figure}
